R for Clinical Study Reports and Submission

### 2021-08-29 tlf-population.Rmd
update minor formating item
pass spell checking

# Table for Analysis Population {#population}

@@

The function can be enhanced in multiple ways, but here we only focus on simplificy and readability.
More details about writting R functions can be found in [Stat454 course](https://stat545.com/functions-part1.html).

>>>>

# Analysis Population {#population}

@@

The function can be enhanced in multiple ways, but here we only focus on simplicity and readability.
More details about writing R functions can be found in [Stat454 course](https://stat545.com/functions-part1.html).
